Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-05-14 inc/model_results/shapes/shapes.tex
tweaks to shapes section

The bunch propagation dynamics for negligible pulse charge density case shown in \ref{fig:compare_shape}\subref{fig:compare_shape_N1} display the trends expected from the initial photoemission conditions.
In particular, in the initially spherical case ($ \xi(0) = 1 $), the transverse bunch width $ \sqrt{2 \sigma_{\smallT}} $ expands approximately twice as rapidly as the longitudinal length $ \sqrt{2 \sigma_{z}} $ due to the factor of two difference in the initial momentum variances $ \Delta p_{\alpha} $ and the artificially zero initial pulse chirp.
Naturally, for initially non-spherical electron bunches, the pulse propagation model also shows that the relative bunch broadening $ \sqrt{ \sigma_{\alpha} / \sigma_{\alpha} (0) } $ for comparable $ \eta_{\alpha} $ is greatest for the smallest initial $ \sigma_{\alpha} (0) $; that is both oblate and prolate pulses are initially driven towards the spherical regime.
In all cases, this intrinsic electron pulse broadening due to non-zero $ \eta_{\alpha} $ generates a momentum chirp across the electron bunch; in the longitudinal dimension the faster electrons photoemitted with larger excess energy leading the slower electrons.

>>>>

The bunch propagation dynamics for the negligible pulse charge density case shown in \ref{fig:compare_shape}\subref{fig:compare_shape_N1} display the trends expected from the initial photoemission conditions.
In particular, in the initially spherical case ($ \xi(0) = 1 $), the transverse bunch width $ \sqrt{2 \sigma_{\smallT}} $ expands approximately twice as rapidly as the longitudinal length $ \sqrt{2 \sigma_{z}} $ due to the factor of two difference in the initial momentum variances $ \Delta p_{\alpha} $ and the artificially zero initial pulse chirp.
Naturally, for initially non-spherical electron bunches, the pulse propagation model also shows that the relative bunch broadening $ \sqrt{ \sigma_{\alpha} / \sigma_{\alpha} (0) } $ for comparable $ \eta_{\alpha} $ is greatest for the smallest initial $ \sigma_{\alpha} (0) $; that is both oblate and prolate pulses are initially driven towards the spherical regime.
In all cases, this intrinsic electron pulse broadening due to non-zero $ \eta_{\alpha} $ generates a momentum chirp across the electron bunch; in the longitudinal dimension the faster electrons, those photoemitted with larger excess energy, lead the slower electrons.
